---
title: "Function_Demos"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function_Demos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Function Demonstrations

This vignette demonstrates the usage of three main functions from the `SA24204134` package: 
`fibonacci_cpp`, and `lasso_elbow`.

---

## Example 1: Fibonacci Sequence with C++

The fibonacci_cpp function calculates the Fibonacci sequence for a given number using a high-performance C++ implementation.

### Code Example
```{r}
# Load the package
library(SA24204134)

n <- 20  # Choose a relatively large value for a meaningful comparison

fibonacci_cpp = fibonacci_cpp(n)
fibonacci_cpp
```




## Example 2: lasso_regression

The function performs LASSO regression on high-dimensional data and selects the regularization parameter using the elbow method.

### Code Example

```{r}
# Example usage:
library(SA24204134)

# Generate dataset and fit Lasso model
result <- generate_lasso_regression(n_samples = 100, n_features = 50, noise_level = 1)

# Display optimal lambda
cat("Optimal lambda:", result$optimal_lambda, "\n")

# Plot Cross-validation error
print(result$cv_error_plot)

```

## Example 3: sparse_matrix_threshold with C++

Here is a more complex Rcpp function example that performs sparse matrix thresholding (setting elements of a matrix below a certain threshold to zero). This operation is particularly useful when working with sparse data, neural network weight matrices, or specific numerical problems.

### Code Example


```{r}
library(SA24204134)

# Create a random matrix
mat <- matrix(rnorm(100), nrow = 10, ncol = 10)

# Apply sparse matrix thresholding
sparse_mat <- sparse_matrix_threshold_cpp(mat, 0.5)

# Print the sparse matrix
print(sparse_mat)

# Verify that all values below the threshold are zero
all(abs(sparse_mat[abs(mat) < 0.5]) == 0)
```


